Assignment 5

### 2015-03-02 rmtw/a5/latex8.tex
review prot0col d0ne
Conducting the study

\documentclass[10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{url}
\usepackage{tabularx}
\usepackage{appendix}

@@

The exclusion critiera were defined as follows: \newline
\begin{itemize}
\item Informal papers (no defined research questions, no methodology)
\item Non-peer reviewed papers (books, white papers etc.)
\end{itemize}

@@

Evaluating the review protocol (5.5)

\SubSection{Conducting}
\textbf{Conducting the review}
\begin{itemize}
\item Identification of research (6.1)

Trial Search, Checking vs already performed studies.
We picked 6 well known studies, our search strings did manage to find them all.

Didn't check other disciplines as the area is not relevant.

Summarise publication bias.

Table, showing what sources we searched, what dates, what strategy, Years covered by search, what journal and conference proceedings were covered.

Justify the when, the where and the how.

\item Selection of primary studies (6.2)
Sources that provide direct evidence about the research question. Refined search criteria here?

\item Study quality assessment (6.3) x

Apply the inclusion and exclusion criteria here, keeping a list of all excluded articles.

Studies not related to Software Engineering were excluded first and as such have not been included in the exclusion list due to their irrelevance.

Cohen Kappa statistic. Initial value here. Disagreements will be discussed and resolved.

@@

Quality of the papers must also be considered before they are examined for use in the study, this is done along with the inclusion and exclusion criteria.

@@

\SubSection{Reporting (probably skip)}
\textbf{Reporting the review}
\begin{itemize}
\item Specifying dissemination mechanisms (7.1)
\item Formatting the main report (7.2)
\item Evaluating the report (7.3)
\end{itemize}

>>>>

\documentclass[10pt,twocolumn]{article} 
\usepackage{latex8}
\usepackage{url}
\usepackage{tabularx}
\usepackage{appendix}
\usepackage{pbox}

@@

The exclusion criteria were defined as follows: \newline
\begin{itemize}
\item Informal papers (no defined research questions, no methodology)
\item Non-peer reviewed papers (books, white papers etc.)
\end{itemize}

@@

The protocol was evaluated by Ioannis Kellaris and Patrik B\"ackstr\"om. The main objective of the review was to ascertain that the current protocol would properly address the research questions. Each step of the review protocol was evaluated based on this criteria.

\SubSection{Conducting the Study}
\textbf{Conducting the review}
\begin{itemize}
\item Identification of research (6.1)

To ensure that our search criteria had be selected correctly, a small trial study was performed to ensure that our criteria could find six predetermined and well known papers which are relevant to our study. %Cite the papers here?

While Kitchenham\cite{keele2007guidelines} suggest the inclusion of papers from related disciplines, this was not undertaken for this study. Other disciplines, while appropriate for some research we shall review, are not appropriate or relevant.

As suggested by Kitchenham\cite{keele2007guidelines}, publication bias is something that we will have to overcome in our study. From our trial study and previous research into related work, it became clear that there seems to exist some bias towards the adoption of MDSD; there are few papers which speak ill of it. To help alleviate this we shall check, but not include, grey literature (non-formally published papers), conference proceedings. We shall also attempt to contact researchers and change agents with experience of implementing MDSD to ascertain if they have unpublished results which can balance the positive bias.

\item Selection of primary studies (6.2)

In order to correctly collect all the relevant papers, a particular search process had to be defined. The table below shows the correlation between the types of sources and how they were searched.

\begin{table}[ht]
	\centering
    \begin{tabular}{ | l | p{5cm} |}
    \hline
    \textbf{Data Source} & \textbf{Data Collected} \\ \hline
    Digital Sources & Database Name \newline Date of Search \newline Year span \\ \hline
    Conference Proceedings & Conference Title \newline Conference Name \newline Journal Name \\ \hline
    Unpublished Studies & Names of those contacted \newline Research websites searched (Date and URL) \\
    \hline
    \end{tabular}
	\caption{Searching Strategies}
\end{table}

The digital libraries, mentioned in section Table 1 were chosen for their extensive catalogues, reliability and availability of the data. Hand searching of journals was not performed as we decided to limit the scope of the search to digital libraries, conferences and other sources.

Given that MDSD is a relatively new process, we have decided to limit the search starting in 1990 to the current date. We feel that this limitation on the search will not hinder our results as we were unable to find any papers published prior to this date concerning MDSD.

The selection criteria for the papers will be further refined during this stage. After applying the initial exclusion and inclusion criteria, we can exclude and include based on practicality. Below is a short list of these criteria.

\begin{itemize}
\item Language
\item Date of publication
\end{itemize}

\item Study Quality Assessment (6.3) x

The Quality of the papers must also be considered before they are examined for use in the study. Determination of paper quality will be performed after initial exclusions and inclusions have been performed. These additional quality checks will seek to eliminate papers with excessive bias, quality of the paper and the reliability of the results.

%Maybe this needs more backup, or some more oomph?

To assess the reliability of the inclusions and exclusions, Fleiss' kappa index will be applied on both researchers findings. All conflicts regarding to acceptance of papers will be discussed and resolved prior to their inclusion in the SLR. Ideally, the kappa rating achieved will be from 0.61 - 0.80 indicating a strong alignment between the researchers.

Furthermore, as per the suggestion from Kitchenham \cite{keele2007guidelines} after the application of the inclusion and exclusion criteria any paper failing to meet these criteria will be retained and shown in the results of the SLR.

%Skipping some steps of this as they don't feel that relevant, discuss with willy.

@@

In order to accurately and objectively collect all data, the use of data collection forms is highly recommended \cite{keele2007guidelines}. These forms will be created and the pilot tested by the researchers taking part in the study. This allows the researchers to discover potential issues before the study takes place, such as ambiguity the data form questions.

The data extraction will be performed by both researchers on each individual study, meaning each study is extracted twice. By doing this, the chance for bias and misinterpretation is reduced. As suggested by kitchenham \cite{keele2007guidelines}, care must be taken to avoid the acceptance of duplicate studies of the same data. In the case of duplication, the most robust study will be chosen.

Data from ongoing studies will be not included in our data extraction. The primary reason behind this stance is that we are interested in the complete adoption of MDSD and as such a study which is either examining the adoption and is half way through will not help us answer this question.

@@

\SubSection{Reporting (probably skip)}
\textbf{Reporting the review}
\begin{itemize}
\item Specifying dissemination mechanisms (7.1)

As the the results will be intended to have some impact upon whether or not MDSD is adopted in practice. As such the results will ideally be disseminated via journals, publications and via web pages to reach a broad audience.

\item Formatting the main report (7.2)
\item Evaluating the report (7.3)
\end{itemize}
